Marlowe: financial contracts on blockchain\thanks{This work is part of the Cardano project and is supported by IOHK,~\url{https://iohk.io}}

### 2018-05-19 tex/paper.tex
minor edits

This paper explores the design of a domain specific language, Marlowe,\footnote{Named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury,  \url{en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains.

In doing this, we are required to refine the model of contracts in a number of ways in order to fit with a radically 
different context. Consider the following example of an ``escrow'' contract so that we can explain the motivation 
more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} 
involves three participants \haskellinline{1}, \haskellinline{2} and \haskellinline{3}. Participant \haskellinline{1} is 
to pay an amount of money to participant \haskellinline{2} on receipt of goods from her. Participant \haskellinline{1} 
pays the money into escrow controlled by participant \haskellinline{3}. There are two options for the money: if two 
participants agree to \haskellinline{pay} it to \haskellinline{2}, that goes ahead; if, on the other hand, two of the 
participants opt to \haskellinline{refund} the money to \haskellinline{1}, that is done instead. The 
\haskellinline{When} construct fires when its first argument -- a condition -- becomes true; the second argument, a 
\haskellinline{Contract} itself, is then performed, and this makes the payment according to the participants' 
\haskellinline{Choice}.

@@

In this section, we explain the detailed behaviour of \haskellinline{Contracts} through a discussion of the \haskellinline{step} function.

>>>>

This paper explores the design of a domain specific language, Marlowe,\footnote{Named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury,  \url{en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains.
In doing this, we are required to refine the model of contracts in a number of ways in order to fit with a radically 
different context.

Consider the following example of an ``escrow'' contract so that we can explain the motivation 
more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} 
involves three participants \haskellinline{1}, \haskellinline{2} and \haskellinline{3}. Participant \haskellinline{1} is 
to pay an amount of money to participant \haskellinline{2} on receipt of goods from her. Participant \haskellinline{1} 
pays the money into escrow controlled by participant \haskellinline{3}. There are two options for the money: if two 
participants agree to \haskellinline{pay} it to \haskellinline{2}, that goes ahead; if, on the other hand, two of the 
participants opt to \haskellinline{refund} the money to \haskellinline{1}, that is done instead. The 
\haskellinline{When} construct fires when its first argument -- a condition -- becomes true; the second argument, a 
\haskellinline{Contract} itself, is then performed, and this makes the payment according to the participants' 
\haskellinline{Choice}.

@@

In this section, we explain the detailed behaviour of contracts by describing how the \haskellinline{step} function operates on each of the constructors of the \haskellinline{Contract}  type.
